Formatting Instructions \\for Authors Using \LaTeX{}

### 2016-05-18 doc/paper.tex
singular pronouns without antecedents

>>>>

With the ALPAC report's pessimistic outlook on MT arguably responsible for sparking decades of fundamental linguistics research in the tradition of Chomsky, it is only fitting that we now bring linguistics back?
No, my Return of the Linguist had more to do with how RBMT systems have fallen out of favor in research
